---
name: Boris Fazio
position: "Data Analyst"
address: "Quantitative methods for public health and biomedical research"
phone: +51 987 807 758
www: bmfazio.github.io
email: "boris.fazio@outlook.com"
#twitter: mariecurie
github: bmfazio
linkedin: bmfazio
date: "`r Sys.setlocale('LC_ALL','English');format(Sys.time(), '%B %Y')`"
output: (function (...) {;template <- here::here("cv-template.tex");vitae::cv_document(..., template = template, citation_package = "biblatex",latex_engine = "xelatex")})
---

#

\begin{changemargin}{1.5cm}
asi que aqui podria hacer una gran descripcion de todos mis logros de la vida y etceras mas propicios de un junco talado en tropical meseta del olvido lejano
\end{changemargin}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)

limape <- "Lima, Perú"
pucp <- "Pontificia Universidad Católica del Perú"
upch <- "Universidad Peruana Cayetano Heredia"
unicef <- "UNICEF"
ciisss <- "Centro de Investigación Interdisciplinaria en Sexualidad, Sida y Sociedad"
minsa <- "Ministerio de Salud"
midis <- "Ministerio de Desarrollo e Inclusión Social"
faspa <- "Facultad de Salud Pública y Administración"

m_stat <- "Masters in Statistics"
m_stat.date <- "Mar. 2017 - Dec. 2018"
m_epid <- "Graduate studies in Epidemiological Research"
m_epid.date <- "Mar. 2015 - Dec. 2015"
b_biol <- "BSc in Biology"
b_biol.date <- "Mar. 2009 - Dec. 2014"


```

# Experience

```{r}
tribble(
  ~ position, ~ company, ~ loc, ~ dates, ~ details,
  "Contractor", unicef, limape, "Aug. 2018 -",
  NA,
  "Data Analyst", minsa, limape, "Oct. 2016 - May. 2018",
  NA,
  "Contractor", midis, limape, "Dec. 2017 - Feb. 2018",
  NA,
  "Research Assistant", paste(faspa, "--", upch), limape, "Dec. 2014 - Dec. 2016",
  NA,
  "Data Manager", ciisss, limape, "Sep. 2015 - Oct. 2016",
  NA
) %>% 
  detailed_entries(company, dates, position, loc, details)
```

# Education

```{r}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
  m_stat, pucp, limape, m_stat.date,
  NA,
  #m_stat, pucp, limape, m_stat.date,
  #"cursos?",
  m_epid, upch, limape, m_epid.date,
  NA,
  b_biol, upch, limape, b_biol.date,
  NA
) %>% 
  detailed_entries(degree, dates, uni, loc, details)
```

# Some stuff about me

 * I poisoned myself doing research.
 * I was the first woman to win a Nobel prize
 * I was the first person and only woman to win a Nobel prize in two different sciences. 