%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\colorlet{awesome}{awesome-red}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{false}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Boris Fazio}{}

\position{Data Analyst}
\address{Quantitative methods for public health and biomedical research}

\mobile{+51 987 807 758}
\email{\href{mailto:boris.fazio@outlook.com}{\nolinkurl{boris.fazio@outlook.com}}}
\homepage{bmfazio.github.io}
\github{bmfazio}
\linkedin{bmfazio}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {October 2021}
    {Boris Fazio~~~·~~~Curriculum Vitae}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{experience}{%
\section{Experience}\label{experience}}

\begin{cventries}
    \cventry{Government Delivery Unit -- Presidencia del Consejo de Ministros}{Information analyst}{}{Sep. 2019 - May. 2020}{\begin{cvitems}
\item Coordinated with technical teams and decisionmakers in order to identify and resolve bottlenecks for prioritized public health interventions
\item Analysis of administrative data and national surveys to support monitoring and evaluation of prioritized interventions
\end{cvitems}}
    \cventry{UNICEF}{Measurement Analyst (Contractor)}{}{Aug. 2018 -}{\begin{cvitems}
\item Integrated data from national surveys and administrative databases to enable calculation of well-being indicators
\item Implemented a reproducible pipeline for data processing and reporting
\item Conducted a review of published literature on the measurement of adolescent well-being
\end{cvitems}}
    \cventry{Ministerio de Salud}{Data Analyst}{}{Oct. 2016 - May. 2018}{\begin{cvitems}
\item Leveraged data from multiple administrative databases to identify over 100 000 children with incomplete anemia treatment
\item Led redesign of KPI monitoring application, offloading data entry tasks from our five person team to over 200 counterparts countrywide
\item Provided statistical support on sampling schemes and sample size selection for national surveys
\item Advised on operational definitions of KPIs for health interventions
\end{cvitems}}
    \cventry{Ministerio de Desarrollo e Inclusión Social}{Data Analyst (Contractor)}{}{Dec. 2017 - Feb. 2018}{\begin{cvitems}
\item Implemented automated reports for monitoring of health interventions
\end{cvitems}}
    \cventry{Facultad de Salud Pública y Administración -- Universidad Peruana Cayetano Heredia}{Teaching Assistant}{}{Mar. 2017 - Dec. 2017}{\begin{cvitems}
\item Tutoring for graduate-level Biostatistics and Epidemiology courses
\item Helped graduate students define a research question and design an analysis plan
\end{cvitems}}
    \cventry{Facultad de Salud Pública y Administración -- Universidad Peruana Cayetano Heredia}{Research Assistant}{}{Dec. 2014 - Dec. 2016}{\begin{cvitems}
\item Generated periodic reports and recommendations to minimize entry errors for ongoing studies
\item Provided logistics support for other researchers
\end{cvitems}}
    \cventry{Centro de Investigación Interdisciplinaria en Sexualidad, Sida y Sociedad}{Data Manager}{}{Sep. 2015 - Oct. 2016}{\begin{cvitems}
\item Automated retention analysis reports for cohort study
\item Advised colleagues on statistical methods for study analysis
\item Cleaned data and improved documentation for existing procedures
\end{cvitems}}
\end{cventries}

\hypertarget{education}{%
\section{Education}\label{education}}

\begin{cventries}
    \cventry{Pontificia Universidad Católica del Perú}{Master in Statistics}{}{April 2021}{}\vspace{-4.0mm}
    \cventry{Universidad Peruana Cayetano Heredia}{Bachelor of Science in Biology}{}{July 2015}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{skills}{%
\section{Skills}\label{skills}}

\begin{cvskills}
\cvskill{Data analysis}{Hierarchical models, survival analysis, structural equation modeling, survey analysis and design}
\cvskill{Programming}{R, SQL, Python, JavaScript}
\cvskill{Languages}{Spanish, English}
\end{cvskills}

\pagebreak

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\begin{cvhonors}
    \cvhonor{}{\textbf{Allan-Blitz LT et al.} \textit{The Development of an Online Risk Calculator for the Prediction of Future Syphilis among a High-Risk Cohort of Men Who Have Sex with Men and Transgender Women in Lima, Peru.} Sexual Health, 2018.}{}{}
    \cvhonor{}{\textbf{García PJ et al.} \textit{Sexual health knowledge and practices and STI/HIV prevalence among long-distance truck drivers in Peru.} SAGE Open Medicine, 2017.}{}{}
    \cvhonor{}{\textbf{Egoavil MS et al.} \textit{Qualitative Study for the Development of a Telemedicine System in Palliative Care.} Palliative Medicine and Hospice Care, 2017.}{}{}
\end{cvhonors}

\end{document}
